### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf
add figures
update

\chapter{Precise Analysis on Chosen-plaintext Attacks}\label{chapter5}
\section{Introduction}
Side-channel attacks allow attackers to infer sensitive information based on the non-functional behaviors of the computer system. Examples of those non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard}. In short, the program has different execution behaviors when it processes various keys. As an attacker, he can infer nontrivial information by observing those secret-dependent behaviors. While separate side-channel attacks may have different forms and patterns, we find a large portion of them share the same fundamental reasons. That is, the memory access pattern is dependent on the original sensitive input.

While removing those dependent memory-access patterns in existing software completely seems impossible, fixing some of the most dangerous leakages appears to be a feasible solution. Previous studies on side-channel detections have shown their effectiveness in finding such code patterns. As a developer, he can run the tool to analyze the side-channels leakages and fix those patterns. However, fixing all those leakages seem impossible. First, side-channels are inevitable. For example, tremendous efforts have been made to remove the side-channel vulnerabilities in cryptography libraries in the past decade. However, we still find that there are plenty of side-channel leakages in the latest version of OpenSSL. Second, many side-channel vulnerable versions usually have better performance, such as the T-table lookup in AES, CRT optimizations in RSA, and Fast Discrete Fourier Transform (FDFT) in many media processing libraries. Third, some developers are not interested in fixing side-channels vulnerabilities unless we can show them an attack demo, even for the cryptography developers. For many non-cryptography developers, side-channels are not in the threat model. However, recent studies have shown a series of attacks on the non-cryptography libraries.

The key to solve the problem is looking for a proper metric to assess the sensitive level of the side-channel leakages. Many side-channel analysis works focus on detecting leakages, which is fine because most side-channel attacks target cryptography libraries. For cryptography libraries, even a minor leakage can be severe because the leakage can reduce the strength of the encryption algorithm. However, many attacks also exploit non-cryptography libraries and applications like machine learning frameworks~\cite{yan2020cache,hong2018security}, graphic libraries~\cite{wang2019unveiling}, spell checking tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on cryptography libraries that exploit one vulnerability each time, attacks on non-cryptography rely on multiple side-channel leakage sites to retrieve more information. Suppose one program has two leakage sites, it is hard to estimate the total effect of those two leakages. Any two leakages have some underlying complex relationships. That is, the two leakages could be completely independent, which means they leak different information. Alternatively, the two leakages could leak the same information. A typical situation, that is, the two leakage sites, can leak some common knowledge. Apart from that, they have their unique leakages. However, no existing tools that can estimate the total effect of multiple leakage sites. For real-world applications with thousands of lines, it is hard to estimate the amount of leaked information. Attackers can guess the values of some temporary values. But those temporary values contain some knowledge of the original secret buffer.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{./figures/channel.pdf}
    \caption{The relationship between the side-channel attack and the channel capacity. For a deterministic program, the side-channel attack can be seen as the communication between the observation ($o \in O$) and the secret ($k \in K$) via a discrete memoryless channel.}
    \label{fig:side_channel}
\end{figure}

@@

\begin{tabular}{cccccccccc}
\toprule
\diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5& 6& 7 &  ...\\ 
\midrule
0 & A &  &  &  &  &  \\
1 &  & A &  &  &  &  \\
2 &  &  & A &  &  &  \\
3 &  &  &  & A &  &  \\
4 &  &  &  &  & A &  \\
5 &  &  &  &  &  & A & \\
6 &  &  &  &  &  & &A \\
7 &  &  &  &  &  &  && A\\ 
\bottomrule
\end{tabular}%
}
\end{minipage}
\caption{A Serious Leakage}\label{fig:example1}
\end{figure}

@@

\begin{tabular}{cccccccccc}
\toprule
\diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5& 6& 7 &  ...\\ 
\midrule
0 & A &  &  &  &  &  \\
1 &  & A &  &  &  &  \\
2 &  &  & A &  &  &  \\
3 & &  &  & A &  &  \\
4 & A &  &  &  &  &  \\
5 &  &  A& &  &  & & \\
6 &  &  & A &  &  & & \\
7 &  & &  &  A&  &  && \\ 
\bottomrule
\end{tabular}%
}
\end{minipage}
\caption{A Minor Leakage. }\label{fig:example2}
\end{figure}
On the other hand, the second example also have a side-channel leakages at line 7. However, the leakage is slightly different. Still, we test the program with input from $0, 1, \dots, 7$. However, we find the attacker can not uniquely determine the secret based on the observation of table $T$. For example. both $0$ and $4$ read the first the item of the table. Therefore, we think the vulnerability is slightly minor than the previous one. Here comes with the definition of the amount of leaked information of the vulnerability.

@@

\includegraphics[width=\columnwidth]{./figures/align.pdf}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{./figures/workflow.pdf}
    \caption{The workflow of \tool{}. We try to divide the \tool{} into three steps to assist the illustration. }\label{fig:workflow}
\end{figure}

@@

\begin{tabular}{ll}  
\toprule
Observation  & P  \\
\midrule
00 & $3/8$   \\
01 & $1/2$   \\
10 & 0 \\
11 & $1/8$\\
\bottomrule
\end{tabular}
}
\end{minipage}
\caption{Example 2}\label{fig:design:example2}
\end{figure}
\end{myexample}

@@

\subsection{Limitation}
\tool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \tool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs. For other libraries like graphic rendering, machine learning, \tool{} is very likely to miss some side-channel vulnerabilities. However, \tool{} is not designed to find side-channel vulnerabilities. The goal of \tool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is a main limitation of \tool{}. However, users of \tool{} should be aware the code coverage problem.

>>>>

\chapter{Precise Analysis on Multiple-trace Attacks}\label{chapter5}
\section{Introduction}
Side-channel attacks allow attackers to infer sensitive information based on the non-functional behaviors of the computer system. Examples of those non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}. In summary, if the program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing those secret-dependent behaviors. While separate side-channel attacks may have different forms and patterns, we find a large portion of them share the same fundamental reasons. That is, the memory access pattern is dependent on the original sensitive input.

While removing those dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be a feasible solution. Previous studies on side-channel detections have shown their effectiveness in finding such code patterns. Developers can run the tool to analyze the side-channels leakages and fix those patterns. However, fixing all those leakages seem impossible for the following reasons. First, side-channels are inevitable. For example, tremendous efforts have been made to remove the side-channel vulnerabilities in cryptography libraries in the past decade. However, we still find that there are plenty of side-channel leakages in the latest version of OpenSSL. Second, many side-channel vulnerable versions usually have better performance, such as the T-table lookups in AES, CRT optimizations in RSA, and Fast Discrete Fourier Transform (FDFT) in many media processing libraries. Third, some developers are not interested in fixing side-channels vulnerabilities unless people can show them an attack demo, even for the cryptography developers. For many non-cryptography developers, side-channels are not in the threat model. However, recent studies have shown a series of attacks on the non-cryptography libraries.

The key to solving the problem is looking for a proper metric to assess the side-channel leakages' sensitive level. Many side-channel analysis tools focus on detecting leakages, which is fine because most side-channel attacks target cryptography libraries. For cryptography libraries, even a minor leakage can be severe because the leakage can reduce the encryption algorithm's strength. However, many attacks also exploit non-cryptography libraries and applications like machine learning applications~\cite{yan2020cache,hong2018security}, graphic libraries~\cite{wang2019unveiling}, spell checking tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on cryptography libraries that exploit one vulnerability at a time, attacks on non-cryptography rely on multiple side-channel leakage sites to retrieve more information. Suppose one program has two leakage sites. It is hard to estimate the total effect of those two leakages. Any two leakages have some underlying complex relationships. That is, the two leakages could be completely independent, which means they leak different information. Alternatively, the two leakages could leak the same information. A typical situation, that is, the two leakage sites, can leak some common knowledge. Apart from that, they have their unique leakages. However, no existing tools that can estimate the total effect of multiple leakage sites. For real-world applications with thousands of lines, it is hard to estimate the amount of leaked information. Attackers can guess the values of some temporary values. But those temporary values contain some knowledge of the original secret buffer.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{./figures/chapter5/channel.pdf}
  \caption{The relationship between the side-channel attack and the channel capacity. For a deterministic program, the side-channel attack can be seen as the communication between the observation ($o \in O$) and the secret ($k \in K$) via a discrete memoryless channel.}
  \label{fig:side_channel}
\end{figure}

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              &   &   &   &   & A &                 \\
        5              &   &   &   &   &   & A &             \\
        6              &   &   &   &   &   &   & A           \\
        7              &   &   &   &   &   &   &   & A       \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A Serious Leakage}\label{fig:example1}
\end{figure}

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              & A &   &   &   &   &                 \\
        5              &   & A &   &   &   &   &             \\
        6              &   &   & A &   &   &   &             \\
        7              &   &   &   & A &   &   &   &         \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A Minor Leakage. }\label{fig:example2}
\end{figure}
On the other hand, the second example also have a side-channel leakages at line 7. However, the leakage is slightly different. Still, we test the program with input from $0, 1, \dots, 7$. However, we find the attacker can not uniquely determine the secret based on the observation of table $T$. For example. both $0$ and $4$ read the first the item of the table. Therefore, we think the vulnerability is slightly minor than the previous one. Here comes with the definition of the amount of leaked information of the vulnerability.

@@

      \includegraphics[width=\columnwidth]{./figures/chapter5/align.pdf}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{./figures/chapter5/workflow.pdf}
  \caption{The workflow of \tool{}. We try to divide the \tool{} into three steps to assist the illustration. }\label{fig:workflow}
\end{figure}

@@

      \begin{tabular}{ll}
        \toprule
        Observation & P     \\
        \midrule
        00          & $3/8$ \\
        01          & $1/2$ \\
        10          & 0     \\
        11          & $1/8$ \\
        \bottomrule
      \end{tabular}
    }
  \end{minipage}
  \caption{Example 2}\label{fig:design:example2}
\end{figure}
\end{myexample}

@@

\tool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \tool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs. For other libraries like graphic rendering, machine learning, \tool{} is very likely to miss some side-channel vulnerabilities. However, \tool{} is not designed to find side-channel vulnerabilities. The goal of \tool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is a main limitation of \tool{}. However, users of \tool{} should be aware the code coverage problem.
